Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2014-10-28 AO_bondedSi.tex
this and prev commit closes #9, DTJ edit to the Abstract

\begin{abstract}
Si direct bonding offers flexibility in the design and development of large Si optics by allowing manufacturers to combine subcomponents with a lossless interface.  The bonding process presents challenges in meeting the performance demands and physical robustness, in particular for cryogenic and space applications.  Air cavities in between the Si interface will have large Fresnel reflections which will interfere as a low-Finesse Fabry-P\`erot etalon.  Even small (35 nm) gaps reduce transmission through a direct bonded Si compound optic by 5\% at $\lambda = $ 1.15 $\mu$m at normal incidence.  Stock near infrared spectrophotometers like the Cary5000 from Agilent offer 0.2\% photometric precision.  We can use instruments like the Cary 5000 to detect and measure gaps as small as 8 nm by measuring transmission as a function of wavelength.  Our approach involves modeling multiple incoherent reflections within the substrate interfaces with a wave transfer matrix, modified for intensities rather than complex amplitudes.  The detection and morphology of minuscule gaps provides valuable feedback in the design of Si direct bonding strategies.
\end{abstract}

>>>>

\begin{abstract}
Silicon direct bonding offers flexibility in the design and development of Si optics by allowing manufacturers to combine subcomponents with a potentially lossless and mechanically stable interface. The bonding process presents challenges in meeting the requirements for optical performance because air gaps at the Si interface cause large Fresnel reflections. Even small (35 nm) gaps reduce transmission through a direct bonded Si compound optic by 5\% at $\lambda = 1.15 \; \mu$m at normal incidence. Understanding the optical effects of such gaps and evaluation of various methods for preventing or eliminating them demands that we have a method for measuring not only the two-dimensional extent of the gaps but also their axial extent.  Existing methods for studying gaps provide only poor measures of this axial extent. We can use such instruments to detect and measure gaps as small as 8 nm by measuring transmission as a function of wavelength. We describe a bond inspection method that makes use of precision transmission spectrophotometry. Our analysis of the spectra then produces accurate estimates of the axial depth of air gaps.  Our approach involves modeling multiple incoherent reflections within the substrate interfaces with a wave transfer matrix, modified for intensities rather than complex amplitudes. We describe the measurement and analysis techniques and demonstrate the validity of the approach by measuring bond gaps of known depths produced by microlithography.
\end{abstract}
